\documentclass[a4paper, 10pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[colorlinks = true,linkcolor = blue,urlcolor  = blue,citecolor = blue,anchorcolor = blue]{hyperref}
\usepackage[usenames]{color}
 \urlstyle{same}
\usepackage{enumitem}

\usepackage{geometry}
\geometry{a4paper,left=1.2in,right=1.2in,top=1in,bottom=1in}

\usepackage{palatino}
\setlist[itemize]{leftmargin=1em}
\setlist[enumerate]{leftmargin=1em}

%\leftmargin=0.25in
%\oddsidemargin=0.25in
%\textwidth=6.0in
%\topmargin=0.25in
%\textheight=9.25in

\raggedright

\pagenumbering{arabic}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
}

\newcommand{\contact}[5]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\begin{center}
			{\Large \scshape {#1}}\\ \smallskip
			{#2}\\ \smallskip
			{#3}\\ \smallskip
			{#4}\\ \smallskip
			{#5}\smallskip
		\end{center}
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.3in}{-0.5in}
  }	
	{\end{changemargin}
}	

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\
	#4\\
}

% END RESUME DEFINITIONS

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{\bf{Cong Ma}
\vspace{6pt}}{\emph{Address: } Jones 313, 5747 South Ellis Avenue,
Chicago, IL 60637}{\emph{Homepage:} \url{https://congma1028.github.io/}}{\emph{Email:} congm@uchicago.edu}



\header{\LARGE{Employment}}
\begin{body}
	\vspace{18pt}
	\textbf{Assistant professor} 
	 \hfill \emph{July~2021 - present} \\
	\begin{itemize}
		\item[-] Department of Statistics and the College, University of Chicago
	\end{itemize}
	
		\textbf{Postdoctoral scholar}\hfill \emph{June~2020 - June~2021} \\
    \begin{itemize}
      \item[-] Department of Statistics and Department of Electrical Engineering and Computer Sciences, University of California, Berkeley
      \item[-] Advisor: Professor \emph{Martin J.~Wainwright}
      %\item GPA: 3.976 / 4.0
    \end{itemize}
\end{body}


\bigskip
\header{\LARGE{Education}}
\begin{body}
	\vspace{18pt}

	\textbf{Ph.D.} in \textbf{Operations Research and Financial Engineering} \hfill \emph{May 2020}
    \begin{itemize}
      \item[-] Princeton University, advised by Professor \emph{Yuxin Chen} and Professor \emph{Jianqing Fan}
      %\item GPA: 3.976 / 4.0
    \end{itemize}
    \textbf{B.E.} in \textbf{Electrical Engineering} \hfill \emph{July 2015} \\
    \begin{itemize}
      \item[-] Tsinghua University
    \end{itemize}
    \textbf{Exchange student} \hfill \emph{Aug.~2013 - Dec.~2013} \\
    \begin{itemize}
      \item[-] School of Electrical and Computer Engineering, {Georgia Institute of Technology}
    \end{itemize}
\end{body}



\bigskip
\header{\LARGE{Research Interests}}
\begin{body}
\vspace{18pt}
Mathematics of data science, transfer learning, reinforcement learning, high-dimensional statistics, large-scale optimization, inference and uncertainty quantification, and their applications to neuroscience and signal processing.
\end{body}



\bigskip
\header{\LARGE{Preprints}}
\begin{body}
	\vspace{18pt}
	\begin{enumerate}[label={[{P}{{\arabic*}}]}]


\item Y.~Gui, \textbf{C.~Ma}, Y.~Zhong, ``Unraveling Projection Heads in Contrastive Learning: Insights from Expansion and Shrinkage,'' 2023.

\item Y.~Gui, R.~F.~Barber, \textbf{C.~Ma}, ``Conformalized Matrix Completion,'' 2023.









	\end{enumerate}
\end{body}


\bigskip
\header{\LARGE{Journal articles}}
\begin{body}
\vspace{18pt}
\begin{enumerate}[label={[{J}{{\arabic*}}]}]


\item \textbf{C.~Ma}, R.~Pathak, M.~J.~Wainwright, ``Optimally Tackling Covariate Shift in RKHS-based Nonparametric Regression,'' \emph{Annals of Statistics},  vol.~51, no.~2, pp.~738-761, 2023.

	
\item Y.~Yang, \textbf{C.~Ma}, {``Optimal Tuning-Free Convex Relaxation for Noisy Matrix Completion,''} accepted to \emph{IEEE Transactions on Information Theory}, 2023. \\

\item P.~Rashidinejad, B.~Zhu, \textbf{C.~Ma}, J.~Jiao, S.~Russel, {``Bridging Offline Reinforcement Learning and Imitation Learning: A Tale of Pessimism,''} \emph{IEEE Transactions on Information Theory},  vol.~68, no.~12, pp.~8156 - 8196, June~2022.

\item \textbf{C.~Ma}, B.~Zhu, J.~Jiao, M.~J.~Wainwright, {``Minimax Off-Policy Evaluation for Multi-Armed Bandits,''} \emph{IEEE Transactions on Information Theory}, vol.~68, no.~8, pp.~5314 - 5339, Mar.~2022. \\


\item T.~Tong, \textbf{C.~Ma}, A.~Prater-Bennette, E.~Tripp, Y.~Chi, {``Scaling and Scalability: Provable Nonconvex Low-Rank Tensor
Estimation from Incomplete Measurements,''} \emph{Journal of Machine Learning Research}, vol.~23, no.~1, pp.~7312-7388, 2022. \\



\item Y.~Chen, Y.~Chi, J.~Fan, \textbf{C.~Ma} (\textbf{alphabetical order}), {``Spectral Methods for Data Science: A Statistical Perspective,''}  \emph{Foundations and Trends in Machine Learning}, 2021. \\

\item Y.~Chen, J.~Fan, \textbf{C.~Ma}, Y.~Yan (\textbf{alphabetical order}), {``Bridging Convex and Nonconvex Optimization in Robust PCA: Noise, Outliers, and Missing Data,''}  \emph{Annals of Statistics}, vol.~49, no.~5, pp.~2948-2971, 2021. \\

\item Y.~Chen, \textbf{C.~Ma}, H.~V.~Poor, Y.~Chen, {``Learning Mixtures of Low-Rank Models,''} \emph{IEEE Transactions on Information Theory}, vol.~67, no.~7, pp.~4613-4636, July 2021. \\






\item T.~Tong, \textbf{C.~Ma}, Y.~Chi, {``Low-Rank Matrix Recovery with Scaled Subgradient Methods: Fast and Robust Convergence Without the Condition Number,''}  \emph{IEEE Transactions on Signal Processing}, vol.~69, no.~3, pp.~2396-2409, 2021. \\







\item J.~Fan, \textbf{C.~Ma}, Y~.Zhong (\textbf{alphabetical order}), {``A Selective Overview of Deep Learning,''} \emph{Statistical Science}, vol.~36, no.~2, pp.~264-290, May 2021 (\textbf{invited overview article}).\\

\item T.~Tong, \textbf{C.~Ma}, Y.~Chi, {``Accelerating Ill-Conditioned Low-Rank Matrix Estimation via Scaled Gradient Descent,''} \emph{Journal of Machine Learning Reseasrch}, vol.~22, no.~150, pp.~1-63, May 2021. \\

\item Y.~Li, \textbf{C.~Ma}, Y.~Chen, Y.~Chi, {``Nonconvex Matrix Factorization from Rank-One Measurements,''} \emph{IEEE Transactions on Information Theory}, vol.~67, no.~3, pp.~1928-1950, March 2021.

\item \textbf{C.~Ma}, Y.~Li, Y.~Chi, {``Beyond Procrustes: Balancing-Free Gradient Descent for Asymmetric Low-Rank Matrix Sensing,''} \emph{IEEE Transactions on Signal Processing}, vol.~69, pp.~867-877, Jan.~2021.


	
\item	\textbf{C.~Ma}, J.~Lu, H.~Liu, {{``Inter-Subject Analysis: A Partial Gaussian Graphical Model Approach,''}}  \emph{Journal of the American Statistical Association}, vol.~116, no.~534, pp.~746-755, 2021. \\

\item Y.~Chen, Y.~Chi, J.~Fan, \textbf{C.~Ma}, Y.~Yan (\textbf{alphabetical order}), {``Noisy Matrix Completion: Understanding Statistical Guarantees for Convex Relaxation via Nonconvex Optimization,''} \emph{SIAM Journal on Optimization}, vol.~30, no.~4, pp.~3098–3121, Oct.~2020. \\

\item \textbf{C.~Ma}, K.~Wang, Y.~Chi, Y.~Chen, {{``Implicit Regularization in Nonconvex Statistical Estimation: Gradient Descent Converges Linearly for Phase Retrieval, Matrix Completion, and Blind Deconvolution,''}}  \emph{Foundations of Computational Mathematics}, vol.~20, no.~3, pp.~451-632, June
2020. \\


\item Y.~Chen, Y.~Chi, J.~Fan, \textbf{C.~Ma} (\textbf{alphabetical order}), {``Gradient Descent with Random Initialization: Fast Global Convergence for Nonconvex Phase Retrieval,''} \emph{Mathematical Programming,} vol.~176, no.~1-2, pp.~5-37, July 2019. \\


\item Y.~Chen, J.~Fan, \textbf{C.~Ma}, Y.~Yan (\textbf{alphabetical order}), {``Inference and Uncertainty Quantification for Noisy Matrix Completion,''} \emph{Proceedings of the National Academy of Sciences~(PNAS)} vol.~116, no.~46, pp.~22931-22937, Nov.~2019 (direct submission). \\




	
\item 
	Y.~Chen, J.~Fan, \textbf{C.~Ma}, K.~Wang (\textbf{alphabetical order}), {{``Spectral Method and Regularized MLE Are Both Optimal for Top-$K$ Ranking,''}} \emph{Annals of Statistics,} vol.~47, no.~4, pp.~2204-2235, Aug.~2019. \\







	
	\item J.~Zhang, J.~Tang, \textbf{C.~Ma}, H.~Tong, Y.~Jing, J.~Li, W.~Luyten, M-F.~Moens, {{``Fast and Flexible Top-$k$ Similarity Search on Large Networks,''}} \emph{ACM Transactions on Information Systems}, vol.~36, no.~2,  pp.~13:1-13:30, Sept.~2017.\\
	
\end{enumerate}
\end{body}

\bigskip
\header{\LARGE{Conference papers}}
\begin{body}
	\vspace{18pt}
	\begin{enumerate}[label={[{C}{{\arabic*}}]}]
	
	\item X.~Xu, Y.~Shen, Y.~Chi, \textbf{C.~Ma}, ``The Power of Preconditioning in Overparameterized Low-Rank Matrix Sensing,'' \emph{International Conference on Machine Learning (ICML)}, 2023.
	

	
	\item I.~Uchendu, T.~Xiao, Y.~Lu, B.~Zhu, M.~Yan, J.~Simon, M.~Bennice, C.~Fu, \textbf{C.~Ma}, J.~Jiao, S.~Levine, K.~Hausman, ``Jump-Start Reinforcement Learning,'' \emph{International Conference on Machine Learning (ICML)}, 2023.
	
		\item Y.~Yang, \textbf{C.~Ma}, {``$O(T^{-1})$ Convergence of Optimistic-Follow-the-Regularized-Leader in Two-Player Zero-Sum Markov Games,''} \emph{International Conference on Learning Representations (ICLR)}, 2023. \\
	
	\item R. Pathak, C. Ma, M. J. Wainwright, {``A New Similarity Measure for Covariate Shift with Applications to Nonparametric Regression''}, \emph{International Conference on Machine Learning (ICML)}, 2022 (long presentation).
	
	\item G.~Li, \textbf{C.~Ma}, N.~Srebro (\textbf{alphabetical order}), {``Pessimism for Offline Linear Contextual Bandits using $\ell_p$ Confidence Sets, ''} \emph{Conference on Neural Information Processing Systems (Neurips)}, 2022.
	\item P.~Rashidinejad, B.~Zhu, \textbf{C.~Ma}, J.~Jiao, S.~Russel, {``Bridging Offline Reinforcement Learning and Imitation Learning: A Tale of Pessimism,''} \emph{Conference on Neural Information Processing Systems (Neurips)}, 2021. \\
	
	\item \textbf{C.~Ma}, Y.~Li, Y.~Chi, {``Beyond Procrustes: Balancing-Free Gradient Descent for Asymmetric Low-Rank Matrix Sensing,''} \emph{Asilomar Conference on Signals, Systems and Computers}, Nov.~2019. \\
	\item 
	Y.~Li, \textbf{C.~Ma}, Y.~Chen, Y.~Chi, {{``Nonconvex Matrix Factorization from Rank-One Measurements,''}} \emph{International Conference on Artificial Intelligence and Statistics (AISTATS)}, Apr.~2019. \\
	
	\item 
	\textbf{C.~Ma}, K.~Wang, Y.~Chi, Y.~Chen, {{``Implicit Regularization in Nonconvex Statistical Estimation: Gradient Descent Converges Linearly for Phase Retrieval and Matrix Completion,''}} \emph{International Conference on Machine Learning (ICML)}, July 2018. \\
	
	\item J.~Zhang, J.~Tang, \textbf{C.~Ma}, H.~Tong, Y.~Jing, J.~Li, {{``Panther: Fast Top-$k$ Similarity Search on Large Networks,''}} \emph{ACM SIGKDD Conference on Knowledge Discovery and Data Mining (KDD)}, Aug.~2015.\\
	
	
	\end{enumerate}
\end{body}


\bigskip
\header{\LARGE{Tutorials}}
\begin{body}

\vspace{18pt}
\begin{enumerate}[label={[{Tut}{{\arabic*}}]}]
\item  {``Nonconvex Optimization for High-Dimensional Signal Estimation: Spectral and Iterative Methods,''} European Signal Processing Conference (EUSIPCO) 2020, together with Y.~Chen and Y.~Chi.
\end{enumerate}

\end{body}


\bigskip
\header{\LARGE{Invited talks}}
\begin{body}
	\vspace{18pt}
	\begin{enumerate}[label={[{T}{{\arabic*}}]}]
	
	\item Allerton Conference on Communication, Control, and Computing, Sept.~2023.
	
	\item IDEAL Annual Meeting, June 2023.
	\item University of Bristol, Statistics, Seminar, Nov.~2022. 
	
	\item SIAM Conference on Mathematics of Data Science, Sept.~2022.
	
	\item UIC, Statistics and Data Science Seminar, Dec.~2021. 
	
	
	\item TTIC, Machine Learning Seminar, Oct.~2021.
	
	\item Informs Annual Meeting, Oct.~2021.
	
	\item UC Berkeley, FODSI Seminar, Apr.~2021. 
	
	\item UC Berkeley, BLISS Seminar, Nov.~2020.
	\item ETH, Young Data Science Researcher Seminar, June~2020.
	\item Georgia Tech, ISyE Seminar, School of Industrial \& Systems Engineering, Feb.~2020.
	\item Columbia University, IEOR Department Seminar, Feb.~2020.
	\item UPenn, Department of Statistics, Feb.~2020.
	\item 'UC Irvine, Department of Statistics, Feb.~2020.
	\item UC Davis, Department of Statistics, Feb.~2020.
	\item Rutgers University, Department of Statistics, Jan.~2020.
	\item University of Chicago, Statistics Colloquium, Jan.~2020.
	\item USC, Department of Data Sciences and Operations, Jan.~2020.
	\item Purdue University, School of Industrial Engineering, Dec.~2019.
	\item University of Maryland, College Park, Statistics Seminar, Dec.~2019.
	\item AMS Fall Eastern Sectional Meeting, Oct.~2019.
	\item Cornell University, Annual Young Researchers Workshop, Oct.~2019.
	\item NYU, Mathematics, Information and Computation (MIC) Seminar, Apr.~2019.
		\item Asilomar Conference on Signals, Systems, and Computers, Pacific Grove, Oct.~2018.
		\item CMU, Energy and Information Systems Seminar, July 2018.
		\item ICML Workshop on Modern Trends in Nonconvex Optimization for Machine Learning, July 2018.
		\item International Conference on Machine Learning (ICML), Stockholm, July 2018.
		\item International Symposium on Mathematical Programming, Bordeaux, July 2018.
		\item Tsinghua University, Department of Electrical Engineering, Jan.~2018.
			
		\item International Conference on Data Science, Shanghai, Dec.~2017.
		\item ICSA Applied Statistics Symposium, Chicago, June 2017.
		
		\end{enumerate}
\end{body}
%
\bigskip
\header{\LARGE{Professional Service}}
\begin{body}
	\vspace{18pt}
	\begin{enumerate}
	\item Co-organizer of \emph{Statistics Colloquium}, Department of Statistics, University of Chicago \hfill Sept. 2022 -- present
	\item Co-organizer of \emph{Wilks statistics seminar}, ORFE, Princeton University \hfill July 2018 -- May 2019
	\item Co-organizer of \emph{$6^{\mathsf{th}}$ Princeton Day of Statistics}, ORFE, Princeton University
%	\item Co-organizer of reading group on mathematical data science, Princeton University \hfill Sept.~2018 -- May~2020
	\item Member of Technical Program Committee for \emph{52nd Annual Conference on Information Sciences and Systems} (\emph{CISS 2018})
	\item Reviewer for the following journals: \emph{Annals of Statistics}, \emph{Journal of the American Statistical Association}, \emph{Statistical Science}, \emph{Bernoulli Journal}, \emph{Biometrika}, \emph{Electronic Journal of Statistics}, \emph{Journal of Computational and Graphical Statistics}, \emph{Operations Research}, \emph{Mathematics of Operations Research}, \emph{Proceedings of the IEEE}, \emph{Journal of Machine Learning Research}, \emph{IEEE Transactions on Signal Processing}, \emph{IEEE Transactions on Information Theory}, \emph{Journal of Business \& Economic Statistics}, \emph{Transactions on Knowledge and Data Engineering}, \emph{SIAM Journal on Mathematics of Data Science}, \emph{Mathematical Programming}
	\item Reviewer for the following conferences: \emph{ACM Symposium on Theory of Computing (STOC)}, \emph{Conference on Neural Information Processing Systems} (\emph{NeurIPS}), \emph{International Conference on Artificial Intelligence and Statistics}, \emph{IEEE International Symposium on Information Theory}, \emph{Annual Conference on Information Sciences and Systems}, \emph{International Conference on Acoustics, Speech, and Signal Processing} (\emph{ICASSP})

	\end{enumerate}
\end{body}

%
\bigskip
\header{\LARGE{Teaching}}
\begin{body}
	\vspace{18pt}
	\begin{enumerate}
	\item Topics in Learning Under Distribution Shifts, Winter 2023
	\item Introduction to Probabilistic Models, Winter 2022, 2023
	\item Topics in Mathematical Data Science: Spectral Methods and Nonconvex Optimization, Fall 2021 
%	\item \emph{Statistical Foundations of Data Science} by Professor J.~Fan, Spring 2019, Head Teaching Assistant
%	\item \emph{Mathematics of High-Dimensional Data} by Professor Y.~Chen, Fall 2018, Head Teaching Assistant
%	\item \emph{Large-Scale Optimization for Data Science} by Professor Y.~Chen, Spring 2018, Head Teaching Assistant
%	\item \emph{Statistical Learning and Nonparametric Estimation} by Professor Han Liu, Spring 2017, Teaching Assistant
%	\item \emph{Analysis of Big Data} by Professor Han Liu, Spring 2017, Teaching Assistant
%	\item \emph{Probability and Stochastic Systems} by Professor Mykhaylo Shkolnikov, Fall 2016, Teaching Assistant
	\end{enumerate}
\end{body}


%\bigskip
%\header{\LARGE{Internship Experience}}
%\begin{body}
%\vspace{18pt}
%\emph{AI Labs, Hudson River Trading, New York, NY} \hfill \emph{June~2019 - Aug.~2019} \\
%
%\end{body}

\bigskip

\header{\LARGE{Awards and Honors}}

\begin{body}
    \vspace{18pt}
    \begin{enumerate}
    \item  Hannan Graduate Student Travel Award, Institute of Mathematical Statistics \hfill{} \emph{2020} \\
    \item {School of Engineering and Applied Science Award for Excellence}, Princeton University \hfill{} \emph{2019}\\
    {\em This award is given to SEAS advanced graduate students who have performed at the highest level as scholars and~researchers.} \\
    \smallskip
    \item {AI Labs Fellowship}, Hudson River Trading  \hfill{} \emph{2019}\\
    \smallskip
   \item {Best Poster Award}, Princeton Day of Optimization  \hfill{} \emph{2018}\\
%    \smallskip
%     \item{Student Travel Award}, $35^{\mathsf{th}}$ International Conference on Machine Learning (ICML)  \hfill{} \emph{2018}\\
%    \smallskip
%     \item{SEAS Travel Grant}, Princeton University  \hfill{} \emph{2018}\\
%     \smallskip
%     \item{SEAS Travel Grant}, Princeton University  \hfill{} \emph{2017}\\
     \smallskip
     \item {ICSA Student Paper Award}, International Chinese Statistical Association  \hfill{} \emph{2017}\\
     \smallskip
     \item  {First Year Engineering Fellowship}, Princeton University \hfill{} \emph{2015}\\
    \smallskip
    \item {Outstanding Academic Performance Scholarship}, Tsinghua University  \hfill{} \emph{2014}\\
    \smallskip
    \item {National Scholarship}, Tsinghua University (Highest honor, 2 out of 118 in department)\hfill{} \emph{2013}\\
    \smallskip
    \item {CNPC Scholarship}, Tsinghua University (Highest honor, only recipient in  department)\hfill{} \emph{2012}
    \end{enumerate}
\end{body}


\end{document}