\documentclass[a4paper, 10pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[colorlinks = true,linkcolor = blue,urlcolor  = blue,citecolor = blue,anchorcolor = blue]{hyperref}
\usepackage[usenames]{color}
 \urlstyle{same}
\usepackage{enumitem}

\usepackage{geometry}
\geometry{a4paper,left=1.2in,right=1.2in,top=1in,bottom=1in}

\usepackage{palatino}
\setlist[itemize]{leftmargin=1em}
\setlist[enumerate]{leftmargin=1em}

%\leftmargin=0.25in
%\oddsidemargin=0.25in
%\textwidth=6.0in
%\topmargin=0.25in
%\textheight=9.25in

\raggedright

\pagenumbering{arabic}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
}

\newcommand{\contact}[5]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\begin{center}
			{\Large \scshape {#1}}\\ \smallskip
			{#2}\\ \smallskip
			{#3}\\ \smallskip
			{#4}\\ \smallskip
			{#5}\smallskip
		\end{center}
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.3in}{-0.5in}
  }	
	{\end{changemargin}
}	

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\
	#4\\
}

% END RESUME DEFINITIONS

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{\bf{Zhen Peng}
\vspace{6pt}}{\emph{Address: } SiYuan Building - 509, No.55, ZhongGuanCun East Road, Beijing 100190, China}{\emph{Homepage:} \url{https://p-opt.github.io/}}{\emph{Email:} pengzhen@lsec.cc.ac.cn}

\header{\LARGE{Employment}}
\begin{body}
	\vspace{18pt}
	\textbf{Postdoc}
	\hfill \emph{Nov.~2023 - present} \\
	\begin{itemize}
		\item[-] Academy of Mathematics and Systems Science, Chinese Academy of Sciences
		\item[-] Advisor: Prof.~\emph{Bin Gao}
	\end{itemize}
\end{body}

\bigskip
\header{\LARGE{Education}}
\begin{body}
	\vspace{18pt}

	\textbf{Ph.D.} in \textbf{Operations Research and Financial Engineering} \hfill \emph{Nov. 2023}
    \begin{itemize}
      \item[-] Beihang University, advised by Professor \emph{Hongyi Li} and Professor \emph{Di Zhao}
      %\item GPA: 3.976 / 4.0
    \end{itemize}
    \textbf{B.E.} in \textbf{Information \& Computing Science } \hfill \emph{July 2017} \\
    \begin{itemize}
      \item[-] Northwest A\&F University
    \end{itemize}
\end{body}

\bigskip
\header{\LARGE{Research Interests}}
\begin{body}
\vspace{18pt}
Optimization on low-rank manifolds and their applications
\end{body}

\bigskip
\header{\LARGE{Publications}}
\begin{body}
	\vspace{18pt}
	{\large Preprints}
	\begin{enumerate}[label={[{P}{{\arabic*}}]}]

\item \textbf{Z.~Peng}, H.~Li, C.~Pan, D.~Zhao, {``Local Linear Convergence Rate of Scaled Gradient Descent for Low-rank Matrix Estimation,''} 2023.\\

	\end{enumerate}
	{\large Journal articles}
	\begin{enumerate}[label={[{J}{{\arabic*}}]}]

\item H.~Li, \textbf{Z.~Peng}, C.~Pan, D.~Zhao, {``Fast gradient method for low-rank matrix estimation,''} \emph{Journal of Scientific Computing}, vol.~96, no.~2, pp.~41, 2023.\\

\item \textbf{Z.~Peng}, H.~Li, , D.~Zhao, C.~Pan, {``Reducing the Dimensionality of SPD Matrices with Neural Networks in BCI,''} \emph{Mathematics}, vol.~11, no.~7, pp.~1570, 2023.\\

% \item \textbf{Z.~Peng} (\textbf{alphabetical order}), {``1,''} accepted to \emph{2}, vol.~51, no.~2, pp.~738-761, 2023.\\
	\end{enumerate}
	{\large Conference papers}

	\begin{enumerate}[label={[{C}{{\arabic*}}]}]
\item H.~Li, Y.~Yang, \textbf{Z.~Peng}, D.~Zhao, {``Stacked autoencoder for wavelet-based the EMI signal analysis,''} In \emph{Proc. - Int. Conf. Artif. Intell. Electromechanical Autom., (AIEA)}, 2021.\\
\item  \textbf{Z.~Peng}, H.~Li, S.~Chen, D.~Zhao, {``EMI signal encoding based on deep auto-encoder combined with wavelet transformation.''} In \emph{Int. Workshop Comput. Sci. Eng., (WCSE)}, 2021.\\
	\end{enumerate}
\end{body}

\bigskip
\header{\LARGE{Presentations}}
\begin{body}
	\vspace{18pt}
	\begin{enumerate}
	\item Stacked autoencoder for wavelet-based the EMI signal analysis
	\begin{itemize}
		\item[-] Artif. Intell. Electromechanical Autom. \hfill{} \emph{May 2021} 
	\end{itemize}
	\end{enumerate}
\end{body}

% \bigskip
% \header{\LARGE{Professional Service}}
% \begin{body}
% 	\vspace{18pt}
% 	\begin{enumerate}
% 	% \item
% 	\item Reviewer for the following journals: \emph{}
% 	% \item Reviewer for the following conferences: \emph{}
% 	\end{enumerate}
% \end{body}

%
\bigskip
\header{\LARGE{Teaching}}
\begin{body}
	\vspace{18pt}
	\begin{enumerate}
	\item \emph{Matrix Theory} by Professor D.~Zhao, Fall 2020 $\sim$ Spring 2022, Teaching Assistant
	\item \emph{Linear Algebra} by Professor H.~Li, Fall 2017 $\sim$ Spring 2021, Teaching Assistant
	\end{enumerate}
\end{body}

\bigskip
\header{\LARGE{Awards and Honors}}
\begin{body}
    \vspace{18pt}
    \begin{enumerate}
	\item {Outstanding Graduate}, Beihang University \hfill{} \emph{2023}
	\item {Outstanding Dissertation Award}, Beihang University \hfill{} \emph{2023}
    \end{enumerate}
\end{body}

\end{document}